%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lachaise Assignment
% LaTeX Template
% Version 1.0 (26/6/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Marion Lachaise & François Févotte
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{The last Home-work} % Title of the assignment

\author{Gandhar Kulkarni (mmat2304)} % Author name and email address

\date{} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{} %Problem 1 
\begin{enumerate}
	\item Since $R$ is a PID, we know that $(a,b)=(d),$ for some $d,a,b \in R.$ Then we have $d=am+bn,$ for some $m,n \in R.$ Now we have a vector 
	$v=[a,b]^T \in R^2 \backslash \{0\}.$ Then we show that there exists a $2x2$ matrix that does what we want by constructing one. Let the desired matrix 
	by be given by $X= \begin{pmatrix}
		x_{11}&x_{21}\\
		x_{12}&x_{22} 	
	\end{pmatrix}.$ Now we have $Xv= [x_{11}a + x_{21}b, x_{12}a+x_{22}b]^T=[d,0]^T.$ Comparing terms, we have $x_{12}a+x_{22}b=0.$ Then we have 
	$x_{12}a=-x_{22}b,$ which implies that $ x_{12}| -b,$ and $x_{22}|a.$ It is easy to see that $x_{12}=-a/d$ and $x_{22}=b/d$ does the trick. For $x_{11}a 
	+ 
	x_{21}b=d,$ see that $x_{11}=m$ and $x_{21}=n$ are good choices, since their linear combination produces $d.$ Thus see that 
		$$X=\begin{pmatrix}
			m&n\\
			-b/d&a/d
		\end{pmatrix} $$ is a matrix that achieves the intended result.
	
	\item The above result shall be of much use to us. We see that we want to send $a_{11}$ to $d,$ that is the gcd of $a_{11}$ and $a_{i1},$ and $a_{i1}$ 
	to $0.$ Let $m,n \in R$ such that $d=a_{11}m+a_{i1}n.$ Define the matrix $\tilde{X}=(x_{kl})$ thus--- $x_{11}=m, x_{1i}=n, x_{i1}=-a_{i1}/d, 
	x_{ii}=a_{11}/d.$ Also we have $x_{kk}=1$ if $k \neq 1,i.$ All other elements are $0.$ Then we have $A'=\tilde{X}A=(a'_{kl}),$ where 
	$a'_{11}=a_{11}m+a_{i1}n,$ $a'_{i1}=(-a_{i1})a_{11}+(a_{11})a_{i1}=0,$ and $a'_{kl}=a_{kl}$ for $k \neq 1,i.$   
	We need to see that this here matrix is invertible. For $\tilde{X}$ a $m \times m$ matrix, we want $\det \tilde{X}.$ We expand the determinant along the 
	first row. Then we have $\det \tilde{X}= m \det \tilde{X}[1|1]+ (-1)^{i+1}((-1)^{i+1}\det \tilde{X}[1|i]).$ $\tilde{X}[1|1]$ is a diagonal matrix with 
	$a_{11}$ on the $a_{ii}$th entry, and $1$ otherwise on the diagonal. Thus $\det \tilde{X}[1|1]=a_{11}.$ $\tilde{X}[1|i])$ is a matrix with $x_{i1}$ at 
	the $(i-1,1)$th entry, with every element below and above it zero. We take the determinant along this column, we have $(-1)^{i-1+1}x_{i1}\cdot \det 
	I_{m-2}=(-1)^{i}x_{i1}.$ Thus see that $\det \tilde{X}=ma_{11}+(-1)^{2i+1}(-a_{i1})=1,$ means that $\tilde{X}$ is invertible. 
	
	\item The above result and the result above that shall be of much use to us. If $A=0,$ then there is nothing to do. We then have $A\neq 0.$ Without loss 
	of generality, we take $a_{11}\neq 0.$ This is because we can shift the row with a non-zero element to the top, then send the column with that element 
	to the first column. Now using the above result, there is a $\tilde{X}_1$ such that $a_{21}=0.$ The value of $a_{11}$ changes. Now we have $\tilde{X}_2$ 
	that sends $a_{31}$ to $0.$ We repeat this process till $a_{i1}=0$ for all $i >1.$ Now we have the first column all zero except for $a_{11}.$ Let  
	$X_1:= \tilde{X}_{i-1}\dots \tilde{X}_1.$ Let us denote $X_1A$ by $A'.$ Then consider $A'^T.$ The first row now becomes the first column, and we can do 
	the same thing that we did earlier, to reduce all elements below $a_{11}$ in $A'^T$ to $0.$ Let that operation be given by the matrix $Y_1.$ Naturally, 
	this matrix is the product of matrices obtained from $j-1$ operations as given in the previous part. Then we take the transpose of the matrix $Y_1 A'^T$ 
	to have $$A''=(Y_1A'^T)^T=(Y_1(X_1A)^T)^T=X_1^TAY_1^T.$$ The matrix we have obtained has no non-zero elements below $a_{11}$ or to its right. 
	
	Now note that we can modify our previous result to the second row. Earlier, we reduced all the leading terms of rows other than the first row to zero, 
	then we did the same with columns. Here we reduce the second terms of the $i$th rows for $i >2,$ then do the same for the columns. We can find a $X_2$ 
	and $Y_2$ both invertible such that $X_2A''Y_2$ has all elements of the type $a_{2j}$ and $a_{i2}$ zero, for $i,j \neq 2.$ Now we have a matrix where 
	$a_{11}$ and $a_{22}$ may or may not be zero, but all elements sharing the same row or column with them is zero. We continue this process for the entire 
	matrix, which gives us at every stage two invertible matrices that do the above reduction. To be precise, we have $X_1,\dots,X_t, Y_1,\dots,Y_t$ where 
	$t=\min(m,n).$ We say $X=X_1\dots X_t,$ and $Y=Y_t^{-1}\dots Y_q^{-1}.$ Then putting all of these results together, we get $ D=XAY^{-1}.$ 
	
	We do not know a priori if $a_{11}|a_{22}|\dots |a_{tt},$ but we can ensure this. We first make sure that $a_{11}|a_{22},$ then the general case is easy 
	to see. We execute the elementary column operation $C_1 \mapsto C_1+C_2.$ Now using the previous result we can change $a_{11}$ to $\gcd(a_{11},a_{22},)$ 
	and $a_{21}$ goes to $0.$ All other terms remain unchanged. We know that $d | a_{22}.$ We repeat this procedure for $d_{ii}$ and $d_{(i+1)(i+1)},$ to 
	get the desired result.
\end{enumerate}
 
\section{} %Problem 2

\section{} %Problem 3
We have $M$ a $R-$module which has itself as a generating set. Then $\pi: R^{\oplus M}\twoheadrightarrow M$ is the surjective map sending $e_m$ to $m.$ We 
see that $\pi(e_{rm}-re_m)=\pi(e_{rm})-r\pi(e_m)=rm-rm=0.$ Also, $\pi(e_{m_1+m_2}-e_{m_1}-e_{m_2})=\pi(e_{m_1+m_2})-\pi(e_{m_1})-\pi(e_{m_2})= 
(m_1+m_2)-m_1-m_2=0.$ Therefore we have $ e_{rm}-re_m \in \ker \pi, $ and $e_{m_1+m_2}-e_{m_1}-e_{m_2} \in \ker \pi.$ Thus we have 
$$(e_{rm}-re_m,e_{m_1+m_2}-e_{m_1}-e_{m_2}) \subseteq \ker \pi.$$ 

To see the other inclusion, let there be some $re_m \in \ker \pi.$ Then we have $\pi(re_m)=rm=0.$ See that we can write $re_m$ as $$re_m=-( 
(e_{rm}-re_m)+(e_{0+0}-e_0-e_0) ),$$ as $e_{rm}=e_0.$ Thus for any general element $\sum re_m \in \ker \phi ,$ we can write the term as a linear combination 
of terms in $\left(e_{rm}-re_m, e_{m_1+m_2}-e_{m_1}-e_{m_2}\right).$ Thus $$(e_{rm}-re_m,e_{m_1+m_2}-e_{m_1}-e_{m_2})= \ker \pi, $$ as required. 
\section{} %Problem 4 
\begin{enumerate}
	\item By the structure theorem for finitely generated modules, we have $N \equiv \frac{\mathbb{Z}}{(a_1)}\oplus \dots \oplus 
	\frac{\mathbb{Z}}{(a_k)}\oplus \mathbb{Z}^d$, where $a_1|a_2|\dots|a_k$ and $N$ is a finitely generated submodule in $\mathbb{Q}.$ Since no element in 
	$\mathbb{Q}$ is a torsion element, we must have $T(N)=\{0\}.$ Thus $N \equiv \mathbb{Z}^d.$ Let $d >1,$ say $d=2.$ Then we have a map $f: \mathbb{Z}^2 
	\rightarrow N$ from $\mathbb{Z}^2$ to $N,$ where $f(1,0)=\frac{p_1}{q_1}$ and $f(0,1)=\frac{p_2}{q_2},$ for some $\frac{p_1}{q_1},\frac{p_2}{q_2} \in 
	\mathbb{Q}.$ Then we have $ f(q_1p_2,-q_2p_1)=0, $ which contradicts the linear independence of $\mathbb{Z}.$ Then $d=0,1,$ which means $N$ is either 
	zero or a cyclic module.
	
	\item We have $N_1,N_2,$ two non-zero submodules of $\mathbb{Q}.$ We have $\frac{p_1}{q_2} \in N_1, \frac{p_2}{q_2} \in N_2.$ See that $ 
	\frac{p_1}{q_1}(q_1p_2)=\frac{p_2}{q_2}(q_2p_1),$ thus $p_1p_2 \in N_1 \cap N_2.$ Thus for any non-zero submodule we can find a non-zero element they 
	have in common. 
	
	\item Let $f: \mathbb{Q} \rightarrow M \equiv \bigoplus_{i=1}^k \frac{\mathbb{Z}}{(a_i)} \oplus \mathbb{Z}^d$ be a $\mathbb{Z}-$linear map. By the 
	structure theorem, we can write $M$ as given. Then we have $f(1)=(m_1,\dots,m_k,n_1,\dots,n_d),$ where $m_1 \in \frac{\mathbb{Z}}{(a_1)}, \dots, m_k \in 
	\frac{\mathbb{Z}}{(a_k)},$ and $n_1,\dots,n_d \in \mathbb{Z}^d.$ 
	
\end{enumerate}
\section{} %Problem 5 
$R^{\oplus X}$ is a free module, for some indexing set $X.$ $M$ is some submodule of $R^{\oplus X}.$ We find a subset $Y \subseteq X$ such that $M \cap 
R^{\oplus Y}$ is free and $B$ is a basis for this free module. Let $(B,Y)$ be such a pair with the given partial order. $\mathbb{T}$ is the poset of all 
such submodules in $R^{\oplus X}.$
\begin{enumerate}
	\item $X$ is non-empty. Then we can pick a singleton subset $ \{x\} \subseteq X.$ $R^{\oplus Y}$ must be a finitely generated module (hence the free 
	module generated by a singleton must be $R$), and hence so must $M \cap R,$ as this is merely an ideal in $R,$ which is an ideal generated by one 
	element. Thus the ideal is isomorphic to $R$ as a module. Thus $R \cong Ra,$ where $(a)=I.$ Thus this is an element of $\mathbb{T},$ which means that 
	$\mathbb{T},$ where this above example corresponds to the element $(R,\{1\}).$ 
\end{enumerate}
\section{} %Problem 6 
\begin{enumerate}
	\item Let $f \in \text{Hom}_{\mathbb{Z}}\left(\frac{\mathbb{Z}}{(n)},\frac{\mathbb{Q}}{\mathbb{Z}}\right).$ Then we have an abelian group, as $ 
	\text{Hom}_{\mathbb{Z}}\left(\frac{\mathbb{Z}}{(n)},\frac{\mathbb{Q}}{\mathbb{Z}}\right)$ is a $\mathbb{Z}-$module ($\mathbb{Z}-$modules and abelian 
	groups are the same).  Elements in $\frac{\mathbb{Q}}{\mathbb{Z}}$ are precisely the elements of $\mathbb{Q} \cap [0,1).$ Then due to the 
	$\mathbb{Z}-$linearity of $f,$ we only need to ask where $1$ is sent to. Let us say that $f(1)=\frac{p}{q}.$ We see that $n \cdot f(1)=f(n)=f(0)=0,$ 
	thus $n \cdot \frac{p}{q}=0.$ This then means that $\frac{np}{q} \in \mathbb{Z} \implies n | q.$ Also see that $qf(1)=p \in \mathbb{Z}.$ Thus $f(q)=0,$ 
	which means that $q \in \ker f.$  
\end{enumerate}
\end{document}

















