\documentclass[letterpaper,11pt,twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\setlist{nosep}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{tikz-cd}
\usepackage[margin=0.9in,
left=1.25in,%
right=1.25in,%
top=1.25in,%
bottom=1.25in
]{geometry}	
%\usepackage{stmaryrd} %For mapsfrom

%\usepackage{quiver}
\usepackage{bm}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{amsbsy}
\usepackage{titlesec}
%\usepackage{yhmath}
%\usepackage{mathabx,epsfig}


%Hyperref Settings------
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={black},
	citecolor={red!50!black}
	urlcolor={green!80!black}
}

%%%%%% TITLE %%%%%

\title{Algebra 2 Homework 7}
%\date{\today}


%MATH BACKGROUND DECLARATORS-------------------------------------------------------
\theoremstyle{proposition}
\newtheorem{proposition}{Proposition}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{remark}{\textbf{Remark}}[section]

\theoremstyle{definition}
\newtheorem{notation}{\textbf{Notation}}[section]

\theoremstyle{definition}
\newtheorem{discussion}{\textbf{Discussion}}[section]

\theoremstyle{lemma}
\newtheorem{lemma}{\textbf{Lemma}}[section]

\theoremstyle{definition}
\newtheorem{example}{\textbf{Example}}[section]

%\theoremstyle{remark}
%\newtheorem*{comment}{\textbf{Comments on Proof Technique}}

\theoremstyle{definition}
\newtheorem{construct}{Construction}[section]

\theoremstyle{corollary}
\newtheorem{corollary}{Corollary}[section]

\theoremstyle{definition}
\newtheorem{caution}{\textbf{Caution}}[section]


\theoremstyle{definition}
\newtheorem{question}{\textbf{Question}}[section]

\theoremstyle{definition}
\newtheorem{para}{}[section]


%--------------------------------------------------------------------------------- SOME USEFUL MACROS.


\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\GL}{\text{\rm GL}}
\newcommand{\Ker}[1]{{\fontfamily{lmss}\selectfont 
		\text{\rm Ker}\left (#1\right )
}}
\newcommand{\nsg}{\trianglelefteq}
\newcommand{\abs}[1]{\left \vert #1 \right \vert}
\newcommand{\gen}[1]{\left\langle #1\right\rangle}
\newcommand{\norm}[1]{\left \vert \left \vert #1 \right \vert \right \vert}
\renewcommand{\div}{\;\vert\;}
\newcommand{\isom}{\cong}
\DeclareMathOperator{\Stab}{\text{\rm Stab}}
\newcommand{\Image}[1]{{\fontfamily{lmss}\selectfont 
		\text{\rm Im}\left (#1\right )
}}
\DeclareMathOperator{\Bij}{\text{\rm Bij}}
\DeclareMathOperator{\acts}{\rotatebox[origin=c]{-90}{$\circlearrowright$}}
\DeclareMathOperator{\Orb}{\text{\rm Orb}}
\DeclareMathOperator{\lcm}{\text{\rm lcm}}
\newcommand{\floor}[1]{\left \lfloor #1 \right \rfloor}
\DeclareMathOperator{\Aut}{\text{\rm Aut}}
\DeclareMathOperator{\Inn}{\text{\rm Inn}}
\DeclareMathOperator{\id}{\text{\rm id}}
\newcommand{\F}{\mathbb{F}}




\begin{document}
	\maketitle
	%\tableofcontents
	\begin{proof}[Solution of problem $1$:]
		Let $\zeta_n$ denote a primitive $n$th root of unity. Then see that $-1$ is a primitive $2$nd root of unity. Also see that $-\zeta_n$ cannot have 
		order $n,$ since it is odd, so $-1^n=-1.$ Thus, its order must be more than $n.$ However, $(-\zeta_n)^{2n}=1,$ so its order must divide $2n.$ The 
		only such number is $2n.$ Since the $n$th cyclotomic extension contains these elements, it must contain the $2n$th roots of unity. 
	\end{proof}
\begin{proof}[Solution of problem $2$:]
	Since $A^k = I$ for some $k \geq 1,$ the minimal polynomial $m(x)$ of $A$ divides $x^k-1.$ Clearly, $x^k-1$ is a polynomial with all distinct roots. The 
	minimal polynomial has no repeated roots, hence it must be diagonalisable. 
	
	For $A= \begin{pmatrix}
		1 & \alpha \\
		0 & 1
	\end{pmatrix},$ see that $A^k=  \begin{pmatrix}
	1 & k\alpha \\
	0 & 1
\end{pmatrix},$ for any $k \in \mathbb{N}.$ This can easily be checked by induction. See that for $k=p,$ we must have $I$ since the field has characteristic 
$p.$ See that the characteristic of $A$ is just $x^2-1=0,$ which gives us $\pm 1$ as the eigenvalues. We see that the $\ker \dim (A-I)= \{ (x,y) \in 
\mathbb{R}^2 \div A-I(x,y)^T=0  \}= \dim(\text{ \textrm span } (1,0))=1,$ while $\ker \dim (A+I)= \{ (x,y) \in \mathbb{R}^2 \div A+I(x,y)^T=0  \}= 
\dim(\text{ \textrm span } (0,0) )=0, $ which clearly does not add up to $2,$ since $1$ and $2$ are not the same number. Thus for $\alpha \neq 0,$ this 
matrix is not diagonalisable. If $\alpha=0,$ in the eigenvalue $-1,$ we would have the null space as $ \text{ \textrm span } (0,1),$ which would give us a 
basis for $\mathbb{R}^2.$
\end{proof}
\begin{proof}[Solution of problem $3$:]
We will make some mention of notation explictly detailing the structure of the Galois group of $K=\mathbb{Q}(\theta, i),$ where $\theta = \sqrt[8]{2}.$ Let 
$\zeta= \frac{1}{2}\sqrt{2}(1+i),$ a primitive $8$th root of unity. This is a group of order $16$ over $\mathbb{Q}.$ Let $\sigma, \tau \in \Aut(K/ 
\mathbb{Q}),$ where $\sigma$ sends $\theta$ to $ \zeta \theta,$ $i$ to $i,$ and $\zeta$ to $\zeta^5.$ The last follows from the first two. Define $\tau$ 
such that it sends $\theta$ to $\theta,$ $i$ to $-i$ and $\zeta $ to $\zeta^7.$ We can then see that $\sigma^8=\tau^2=e,$ the identity automorphism. Also 
see that $ \sigma \tau == \tau \sigma^3,$ which can be checked by brute force. This completely characterises the Galois Group. 

Now see that by the fundamental theorem of Galois theory, the subgroups corresponding to $F_1,$ $F_2,$ and $F_3$ are $\gen{\sigma}, \gen{\sigma^2, \tau}$ , 
and $ \gen{\sigma^2, \tau \sigma^3}.$ 

Since $F_1$ is the fixed field of $\gen{\sigma},$ we have $K^{F_1} \cong \mathbb{Z}_8.$ In the second case, the fixed field corresponds to the subgroup 
$\gen{\sigma^2, \tau}.$ We have $(\sigma^2)^4=\tau^2=e,$ and $\sigma^2 \tau = \tau \sigma^{-2},$ which is the presentation for $D_8.$ The subgroup 
corresponding to $F_3$ is $\gen{\sigma^2, \tau \sigma^3}.$ See that there is more than one element of order $4$ in the group. The only such group is $Q_8.$
\end{proof}
\begin{proof}[Solution of problem $4$:]
		We can see that $x^4-14x^2+0=0$ is solved as a quadratic in $x^2,$ that is, $x^2= 7 \pm 2 \sqrt{10}.$ 
	We can write $7 -2 \sqrt{10}= 7-2\sqrt{10}\frac{7+2\sqrt{10}}{7+2\sqrt{10}}= \frac{9}{7+2\sqrt{10}}.$ 
	Then we can see that $x= \pm \sqrt{7+2\sqrt{10}}, \pm \frac{3}{\sqrt{7+2\sqrt{10}}}.$ All of these roots lie in $K=\mathbb{Q}(\sqrt{7+2\sqrt{10}}).$
	
	We propose that this field is Galois. The minimal polynomial for $\sqrt{7+2\sqrt{10}}$ is all in $K,$ thus it is normal, since it contains all of its 
	conjugates. It is also clear that none of the roots are repeated, so the extension is separable. Thus $K$ is the Galois splitting field.
\end{proof}
\begin{proof}[Solution of problem $5$:]
	\begin{enumerate}
		\item $[K:F]=n < \infty,$ then we say that $K$ is represented as by a finite $F-$basis, by $\{b_1,\dots, b_n\}.$ 
		Let $x \in K,$ where  $x= \sum_{i=1}^{n}c_ib_i,$ where $c_i \in F$ for $i=1,\dots,n.$
		Now we have $\alpha \cdot x= \sum_{i=1}^{n}c_i (\alpha \cdot b_i).$ Since $\alpha \cdot b_i \in K,$ $\alpha \cdot b_i= \sum_{j=1}^{n} a_{ji} b_j.$ 
		Then we can put this in matrix form, by $T_{\alpha}:= (a_{ji}).$ By this, it is clear that $T_{\alpha}$ is a linear transformation, since it can be 
		written as a matrix.
		
		\item See that $m(x)= x^d + a_{d-1}x^{d-1}+ \dots + a_0$ is the minimal polynomial of $\alpha,$ and $f(x)$ is the minimal polynomial of 
		$T_{\alpha}.$ We know that $T_{\alpha}$ is a root of $m(x),$ and since $m(x) | f(x),$ since $f(x)$ also has $T_{\alpha}$ as a zero, and $f(x)$ is 
		irreducible, then they must be equal.
		
		\item See that the multiplication operator has a minimal polynomial $m(x),$ and characteristic polynomial $c(x).$ They must have the same roots, and 
		since $m(x)$ is irreducible, we must have $c(x)=m(x)^{n/d},$ comparing the degrees. Then comparing terms, we have $Tr(\alpha) = 
		\frac{-n}{d}a_{d-1}=-b_{n-1}= Tr(T_{\alpha})$, and $N(\alpha) = (-1)^{n}a_{d-1}^{n/d}=(-1)^n b_0= \det T_\alpha.$ 
		
		
	\end{enumerate}
\end{proof}
\begin{proof}[Solution of problem $6$:]
	We have proven in the previous assignment that $f(x)=x^p-x-a$ is irreducible over $\mathbb{F}_p,$ and that it is separable.
	We know that if $\alpha$ is a root, then so is $\alpha + 1.$ So it is easy to see that the automorphism $\sigma: x \mapsto x+1 $ is an automorphism. 
	Clearly, $\sigma^p=e.$ Since these are $p$ such automorphisms $\sigma^i,$ for $0 \leq i \leq p-1,$ then the Galois group must be cyclic.
\end{proof}
\begin{proof}[Solution of problem $7$:]
	In $E=\mathbb{Q}(\sqrt{1+\sqrt{2}}),$let $x= \sqrt{1 + \sqrt{2}}.$ Then $x(x^2-1)^2=2.$ We get that $x^4-2x^2-1=0.$ We can explicitly see that none of 
	its roots are rational, so the polynomial we have must be the minimal polynomial. We can calculate the conjugates, which are $$\pm \sqrt{1+ \sqrt{2}}, 
	\pm i \frac{1}{\sqrt{1+ \sqrt{2}}}.$$ So it is easy to see that $i$ is missing. Thus, by adjoining $i,$ we can have a normal and separable extension 
	containing $\sqrt{1+ \sqrt{2}}.$ We propose that $K=\mathbb{Q}(\sqrt{1+ \sqrt{2}},i)$ is the Galois extension. We know $K$ contains all the conjugates, 
	so the Galois field must be sandwiched between $K$ and $F.$ But since $[K:F]=2,$ which is prime, we must have that either the field is equal to $E$ or 
	$F,$ and it cannot be $F,$ since the imaginary conjugates are not in $F,$ the Galois closure must be $E.$
\end{proof}
\begin{proof}[Solution of problem $8$:]
	If $p \div n,$ then $\sum_{i=1}^{p-1} \epsilon_i^n = \sum_{i=1}^{p-1} 1= p-1. $
	Else, let $\epsilon_j = e^{2\pi ij/p}$ for $1 \leq i \leq n-1,$ then we have 
	$$ \sum_{i=1}^{p-1} \epsilon_i^n= \sum_{i=1}^{p-1} \epsilon_i^{ni}= \frac{\epsilon_i^{np}- \epsilon_i^n}{\epsilon_i^n-1}=-1. $$
\end{proof}
\begin{proof}[Solution of problem $9$:]
	If $\mathbb{Q}(\zeta_n)$ contained $\mathbb{Q}(\sqrt[3]{2}),$ then it must also contains its Galois closure, $\mathbb{Q}(\sqrt[3]{2}, \omega).$ The 
	Galois group of this field is $S_3,$ a non-abelian group contained in $\mathbb{Q}(\zeta_n),$ which must have a abelian Galois group, which is 
	impossible. 
\end{proof}

\end{document}